$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-09-16 paper/paper.tex
Clarify instantiations in the example

The receiver process $R$, defined below, receives data twice on a channel $c$ and then terminates.
\begin{flalign*}
  & \func{recv} \; : \; \Var_n \to \Process_n & \\
  & \func{recv} \; c \; = \recv{c}{} (\recv{\suc c} \PO) \\
\end{flalign*}

The sender processes $S_1$ and $S_2$, defined below, create a new channel that acts as the data that is being sent, send it over the channel $c$, and then terminate.
\begin{flalign*}
  & \func{send} \; : \; \Var_n \to \Process_n & \\
  & \func{send} \; c = \new{} \send{\suc c}{\constr{0}} \PO \\
\end{flalign*}

The courier process $C$, defined below, sequentially receives on the two input channels $in0$ and $in1$, and then outputs the two pieces of received data on the output channel $out$.
\begin{flalign*}
  & \func{carry} \; : \; \Var_n && \to \Var_n \to \Var_n \to \Process_n & \\
  & \func{carry} \; in0 \; in1 \; out \; &&= \\
  & && \recv{in0}{} \\
  & && \recv{(\suc \; in1)}{} \\
  & && \send{(\suc \suc \; out)}{\suc \constr{0}} \\
  & && \send{(\suc \suc \; out)}{\constr{0}} \PO \\
\end{flalign*}

@@

[ALIGN FIG AND PROCESSES IN PARTICULAR send c and send x,y in THE FIGURE]

>>>>

The receiver process $R$, defined below and instantiated as $\func{recv} \; z$, receives data twice on a channel $c$ and then terminates.
\begin{flalign*}
  & \func{recv} \; : \; \Var_n \to \Process_n & \\
  & \func{recv} \; c \; = \recv{c}{} (\recv{\suc c} \PO) \\
\end{flalign*}

The sender processes $S_1$ and $S_2$, defined below and instantiated as $\func{send} \; x$ and $\func{send} \; y$, create a new channel that acts as the data that is being sent, send it over the channel $c$, and then terminate.
\begin{flalign*}
  & \func{send} \; : \; \Var_n \to \Process_n & \\
  & \func{send} \; c = \new{} \send{\suc c}{\constr{0}} \PO \\
\end{flalign*}

The courier process $C$, defined below and instantiated as $\func{carry} \; x \; y \; z$, sequentially receives on the two input channels $in0$ and $in1$, and then outputs the two pieces of received data on the output channel $out$.
\begin{flalign*}
  & \func{carry} \; : \; \Var_n && \to \Var_n \to \Var_n \to \Process_n & \\
  & \func{carry} \; in0 \; in1 \; out \; &&= \\
  & && \recv{in0}{} \\
  & && \recv{(\suc \; in1)}{} \\
  & && \send{(\suc \suc \; out)}{\suc \constr{0}} \\
  & && \send{(\suc \suc \; out)}{\constr{0}} \PO \\
\end{flalign*}

@@
